No proof nets for MLL with units\\[5pt]\Large Proof equivalence in MLL is \textsc{pspace}-complete

### 2014-01-18 main/LICS.tex
added octopus arithmetic to "notation"

We will use a concise diagrammatic notation for sequents and proof nets.
%
The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively.
%
%
%% NEW
%
Formulae related by a tensor will be connected by edges.
%
Formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula.
%
For example, the following denote the same sequent:
\[
	\bot\tn\bot,\bot\tn\bot,\1,(\1\parr\1\parr\1)\tn\bot
\]
\[
\begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\draw (0,0) node[bullet] (a) {} -- (1,0) node[bullet] (b) {} (2,0) node[bullet] (c) {} -- (3,0) node[bullet] (d) {};
	\node[circ] (1) at (4,0) {};
	\node[circ] (2) at (5.25,0) {}; \node[circ] (3) at (6.25,0) {}; \node[circ] (4) at (7.25,0) {};
	\draw[rounded corners] (4.75,-1) rectangle (7.75,1);
	\draw (7.75,0) -- (8.75,0) node[bullet] (e) {};
\end{tikzpicture}
\]
The links of a proof net are added to the sequent as colored arrows.
%
The following example is a proof net for the above sequent.
\[
\begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\node[circ] (1) at (6,0) {};
	\draw (0,0) node[bullet] (a) {} -- (1,0) node[bullet] (b) {} (3,0) node[bullet] (c) {} -- (4,0) node[bullet] (d) {};
	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
	\draw[rounded corners] (0,2) rectangle (4,4);
	\draw (4,3) -- (5,3) node[bullet] (e) {};
	\begin{scope}[thepink,->]
			\draw[bend right=10] (a) to (2.center);
			\draw[bend right=10] (b) to (3.center);
			\draw[bend left=10]  (c) to (3.center);
			\draw[bend left=10]  (d) to (4.center);
			\draw[bend right=10] (e) to (1.center);
	\end{scope}
\end{tikzpicture}
\]

We will denote by $A^n$ the sequent consisting of $n$ occurrences of a formula $A$.
%
Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\parr\cdots\parr A_n$.
%
In diagrammatic notation, a big disc will represent an $n$-ary tensor over only $\bot$-formulae, $\bigtn(\bot^n)$, and a big circle will represent an $n$-ary par over only $1$-formulae, $\bigparr(\1^n)$.
%
A linking between $\bigtn(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated below.
\[
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[big_] (A) at (-1,2) {};
	\node[big1] (!) at (-1,0) {};
	\node at (.5,1) {$\coloneq$};
	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (5,2) -- (6,2) node[bullet] (c) {}; 
	\node[circ] (1) at (2,0) {}; \node[circ] (2) at (3,0) {}; \node[circ] (3) at (6,0) {};
	\draw[dotted] (4,2)--(5,2) (4,0)--(5.1,0);
	\begin{scope}[thepink,->]
			\draw[big>] (A) to (!.center);
			\draw[bend right=10] (a) to (1.center);
			\draw[bend right=10] (b) to (2.center);
			\draw[bend right=10] (c) to (3.center);
	\end{scope}
\end{tikzpicture}
\]

That two vertices in a proof net or a switching graph are connected will be indicated via a dashed edge, as illustrated below.
\[
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[bullet] (a) at (0,0) {}; \node[bullet] (b) at (2,0) {}; \draw[dashed] (a)--(b);
\end{tikzpicture}
\qquad
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[circ] (a) at (0,0) {}; \node[circ] (b) at (2,0) {}; \draw[dashed] (a)--(b);
	%\coordinate (a') at ($(a) + (.6,0)$); \coordinate (b') at ($(b) + (-.6,0)$);
	%\draw[thepink,dashed] (a')--(b'); \draw[thepink,->] (a')--(a.center); \draw[thepink,->] (b')--(b.center);
\end{tikzpicture}
\]

@@

@@

The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
%
In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$ and re-attaching all arcs connecting to removed vertices to $v$.
%

[[ ADD ILLUSTRATED EXAMPLE ]]

%
The contraction of scopes may replace the switching condition as a correctness criterion.
%
The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.

@@

[[ IDEA: the following could help simplify octopus-arithmetic ]]

@@

An unbalanced sequent is uninhabited: a positive balance guarantees a cycle in any switching graph, for any linking, while a negative balance similarly guarantees disconnectedness.

An early conjecture of Girard, which turned out to be false, was that a sequent is inhabited if and only if it is balanced. [[FIND CITATION (probably TCS87)]]

@@

We will demonstrate the \textsc{pspace}-hardness of MLL proof equivalence by an encoding of partial \textsc{ncg}-reconfiguration in MLL.

@@

\begin{definition}
\label{def:standard linkings}
For a weight element $W=W_n(i,j)=A\parr B\parr C$,
\begin{enumerate}
	\item
for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and the remaining $\bot$-occurrences in $A,B,C$ to the remaining $\1$-occurrences in $X,Y$;
	\item
for $C=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,C$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
	\item
the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ each to the first $\1$, and the remaining $\bot$-occurrences to the remaining $\1$-occurrences.
\end{enumerate}
\end{definition}

@@

\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[circ] (1) at (-.25,0) {};
	\node[big1] (2) at (1,0) {};
	\node[big1] (3) at (2.5,0) {};
	\node[big1] (4) at (5.5,0) {};
	\draw[rounded corners] (-1,-1) rectangle (3.5,1) (4.5,-1) rectangle (6.5,1);
	\draw (3.5,0)--(4.5,0);
	%
	\draw (-.25,4) node[bullet] (a) {} -- (.75,4) node[big_] (A) {};
	\draw (2.25,4) node[bullet] (b) {} -- (3.25,4) node[big_] (B) {};
	\node[big_] (C) at (5.5,4) {};
	\draw[rounded corners] (-1,3) rectangle (6.5,5);
	%
	\begin{scope}[thepink,->]
		\draw[bend right=5] (a) to (1);
		\draw[bend right=10] (b) to (1);
		\draw[big>,bend left=25] (A) to (2);
		\draw[big>,bend left=20] (B) to (3);
		\draw[big>,bend left=15] (C) to (4);
	\end{scope}
\end{tikzpicture}
\qquad
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[circ] (1) at (.75,0) {};
	\node[big1] (2) at (2,0) {};
	\node[big1] (3) at (3.5,0) {};
	\node[big1] (4) at (5,0) {};
	%
	\draw ( 0  ,4) node[bullet] (a) {} -- ( 1  ,4) node[big_] (A) {};
	\draw ( 2.5,4) node[bullet] (b) {} -- ( 3.5,4) node[big_] (B) {};
	\draw ( 5  ,4) node[bullet] (c) {} -- ( 6  ,4) node[big_] (C) {};
	\draw[rounded corners] (-.5,3) rectangle (7,5);
	\path (0,-1) -- (1,-1);
	%
	\begin{scope}[thepink,->]
		\draw[bend right=5] (a) to (1);
		\draw[bend right=10] (b) to (1);
		\draw[bend right=15] (c) to (1);
		\draw[big>,bend left=25] (A) to (2);
		\draw[big>,bend left=20] (B) to (3);
		\draw[big>,bend left=15] (C) to (4);
	\end{scope}
\end{tikzpicture}

>>>>

We will use a concise diagrammatic notation for sequents and proof nets.
%
The units $1$ and $\bot$ are represented by a circle $\circ$ and a disc $\bullet$ respectively;
%
formulae related by a tensor will be connected by edges; 
and
formulae related by a par will be juxtaposed, and collected in a box when a par-formula is an immediate subformula of a tensor-formula.
%
For example, the following denote the same sequent:
\[
	\bot\tn\bot,\bot\tn\bot,\1,(\1\parr\1\parr\1)\tn\bot
\]
\[
\begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\draw (0,0) node[bullet] (a) {} -- (1,0) node[bullet] (b) {} (2,0) node[bullet] (c) {} -- (3,0) node[bullet] (d) {};
	\node[circ] (1) at (4,0) {};
	\node[circ] (2) at (5.25,0) {}; \node[circ] (3) at (6.25,0) {}; \node[circ] (4) at (7.25,0) {};
	\draw[rounded corners] (4.75,-1) rectangle (7.75,1);
	\draw (7.75,0) -- (8.75,0) node[bullet] (e) {};
\end{tikzpicture}
\]
The links of a proof net are added to the sequent as colored arrows.
%
The following example is a proof net for the above sequent.
\[
\begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\node[circ] (1) at (6,0) {};
	\draw (0,0) node[bullet] (a) {} -- (1,0) node[bullet] (b) {} (3,0) node[bullet] (c) {} -- (4,0) node[bullet] (d) {};
	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
	\draw[rounded corners] (0,2) rectangle (4,4);
	\draw (4,3) -- (5,3) node[bullet] (e) {};
	\begin{scope}[thepink,->]
			\draw[bend right=10] (a) to (2.center);
			\draw[bend right=10] (b) to (3.center);
			\draw[bend left=10]  (c) to (3.center);
			\draw[bend left=10]  (d) to (4.center);
			\draw[bend right=10] (e) to (1.center);
	\end{scope}
\end{tikzpicture}
\]

We will denote by $A^n$ the sequent consisting of $n$ occurrences of a formula $A$.
%
Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\parr\cdots\parr A_n$.
%
In diagrammatic notation, a big disc will represent an $n$-ary tensor over only $\bot$-formulae, $\bigtn(\bot^n)$, and a big circle will represent an $n$-ary par over only $1$-formulae, $\bigparr(\1^n)$.
%
A linking between $\bigtn(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated below.
\[
\begin{tikzpicture}[x=-5mm,y=5mm,octo]
	\node[big_] (A) at (-1,2) {};
	\node[big1] (!) at (-1,0) {};
	\node at (.5,1) {$\Rightarrow$};
	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (5,2) -- (6,2) node[bullet] (c) {}; 
	\node[circ] (1) at (2,0) {}; \node[circ] (2) at (3,0) {}; \node[circ] (3) at (6,0) {};
	\draw[dotted] (4,2)--(5,2) (4,0)--(5.1,0);
	\begin{scope}[thepink,->]
			\draw[big>] (A) to (!.center);
			\draw[bend right=10] (a) to (1.center);
			\draw[bend right=10] (b) to (2.center);
			\draw[bend right=10] (c) to (3.center);
	\end{scope}
\end{tikzpicture}
\]
Two formulae $\bigtn(\bot^{i+1})$ and $\bigtn(\bot^{j+1})$ may together connect to a formula $\bigparr(\1^{i+j+1})$, as illustrated below for $i=2$ and $j=3$.
%
Nodes will be labelled $i'$ for $i+1$, so that both the abbreviated formulae and the arithmetic of connecting them remain intuitive.
%
\[
\vc{
  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\draw (0,0) node[bullet] (a) {}--
		  (1,0) node[bullet] (b) {}--
		  (2,0) node[bullet] (c) {};
	\draw (4,0) node[bullet] (d) {}--
		  (5,0) node[bullet] (e) {}--
		  (6,0) node[bullet] (f) {}--
		  (7,0) node[bullet] (g) {};
	\foreach \i in {1,...,6} {\node[circ] (\i) at (\i,3) {};}
	\begin{scope}[thepink,->]
			\draw[bend right=10] (a) to (1);
			\draw[bend right=10] (b) to (2);
			\draw[bend right=10] (c) to (3);
			\draw[bend left=10]  (d) to (3);
			\draw[bend left=10]  (e) to (4);
			\draw[bend left=10]  (f) to (5);
			\draw[bend left=10]  (g) to (6);
	\end{scope}
  \end{tikzpicture}
}
\quad\Rightarrow\quad
\vc{
  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\node[big_] (A) at (-1,0) {$2'$};
	\node[big_] (B) at ( 1,0) {$3'$};
	\node[big1] (!) at ( 0,3) {$5'$};
	\begin{scope}[thepink,->,big>]
		\draw[bend right=15] (A) to (!);
		\draw[bend left=15]  (B) to (!);
	\end{scope}
  \end{tikzpicture}
}
\]

Finally, that two vertices in a proof net or a switching graph are connected will be indicated via a dashed edge, as illustrated below.
\[
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[bullet] (a) at (0,0) {}; \node[bullet] (b) at (2,0) {}; \draw[dashed] (a)--(b);
\end{tikzpicture}
\qquad
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[circ] (a) at (0,0) {}; \node[circ] (b) at (2,0) {}; \draw[dashed] (a)--(b);
	%\coordinate (a') at ($(a) + (.6,0)$); \coordinate (b') at ($(b) + (-.6,0)$);
	%\draw[thepink,dashed] (a')--(b'); \draw[thepink,->] (a')--(a.center); \draw[thepink,->] (b')--(b.center);
\end{tikzpicture}
\]

@@

To conclude this section we will discuss (and adapt) some convenient standard notions for MLL proofs and proof nets.

@@

The scopes of a par correspond to the possible subproofs of its introduction rule in a sequentialisation of the proof net that it occurs in.
%
In the graph of a proof net, the scope of a par $\named v\parr$ may be \emph{contracted} to a single vertex $v$ by removing all vertices except $v$,  and re-attaching the edges of any removed vertices to $v$.
%
In the example below, the kingdom of a (ternary) par is indicated (left) and contracted (right).
\[
\begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {}
		  (.25,0) node[bullet] (a) {} -- (1.25,0) node[bullet] (b) {}
		  ( 2.75,0) node[bullet] (c) {} -- (3.75,0) node[bullet] (d) {};
	\node[circ] (0) at (5.75,0) {};
	\node[circ] (1) at (-1,3) {};
	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
	\draw[rounded corners] (0,2) rectangle (4,4);
	\draw (4,3) -- (5.5,3) node[bullet] (e) {};
	\begin{scope}[thepink,->]
			\draw[bend right=10] (x) to (1);
			\draw[bend right=20] (y) to (2);
			\draw[bend right=10] (a) to (2);
			\draw[bend right=10] (b) to (3);
			\draw[bend left=10]  (c) to (3);
			\draw[bend left=10]  (d) to (4);
			\draw[bend right=10] (e) to (0);
	\end{scope}
	\draw[dashed,rounded corners] (-.25,-.5) rectangle (4.25,4.25);
\end{tikzpicture}
\qquad\qquad
\begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\draw (-2.25,0) node[bullet] (x) {} -- (-1.25,0) node[bullet] (y) {};
	\node[circ] (0) at (3,0) {};
	\node[circ] (1) at (-1,3) {};
	\node[draw,rounded corners,minimum size=16pt] (box) at (1,3) {};
	\draw (box)--(3,3) node[bullet] (e) {};
	\begin{scope}[thepink,->]
			\draw[bend right=10] (x) to (1);
			\draw[bend right=20] (y) to (box);
			\draw[bend right=10] (e) to (0);
	\end{scope}
	\path (0,4.25)--(1,4.25);
\end{tikzpicture}
\]
%
The contraction of scopes may replace the switching condition as a correctness criterion.
%
The following is a variant of the local retraction algorithm by Danos \cite{Danos-1990}.

@@

Finally, the standard notion of \emph{balance} is useful in constructing proof nets without $\parr$-connectives

@@

An unbalanced sequent is uninhabited: a positive balance guarantees a cycle in any switching graph, for any linking, while a negative balance similarly guarantees disconnectedness.
%
%An early conjecture of Girard, which turned out to be false, was that a sequent is inhabited if and only if it is balanced. [[FIND CITATION (probably TCS87)]]
%

@@

We will demonstrate the \textsc{pspace}-hardness of MLL proof equivalence by an encoding of partial \textsc{ncg}-reconfiguration in MLL proof nets.

@@

\begin{definition}
\label{def:standard linkings}
For a weight element $W=W_n(i,j)=A\parr B\parr C$,
\begin{enumerate}
	\item
for a constraint element $C=C_n(i)=X\tn Y$, the \emph{standard linking} for the sequent $W,C$ links the first $\bot$ in $A$ to the first $\1$ in $X$, the first $\bot$ in $B$ and $C$ each to the first $\1$ in $Y$, and each remaining $\bot$ in $A,B,C$ to a remaining $\1$ in $X,Y$ in their order of occurrence;
	\item
for $C=C_n(j)=X\tn Y$, the \emph{standard linking} for $W,C$ is defined as above, except the first $\bot$ in $B$ links to the first $\1$ in $X$;
	\item
the \emph{standard linking} for the sequent $W,\1^{3n+4}$ links the first $\bot$ in $A$, $B$, and $C$ to the first $\1$, and each remaining $\bot$ to a remaining $\1$ in order of occurrence.
\end{enumerate}
\end{definition}

@@

\[
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[circ] (1) at (-.25,0) {};
	\node[big1] (2) at (1,0) {};
	\node[big1] (3) at (2.5,0) {};
	\node[big1] (4) at (5.5,0) {};
	\draw[rounded corners] (-1,-1) rectangle (3.5,1) (4.5,-1) rectangle (6.5,1);
	\draw (3.5,0)--(4.5,0);
	%
	\draw (-.25,4) node[bullet] (a) {} -- (.75,4) node[big_] (A) {};
	\draw (2.25,4) node[bullet] (b) {} -- (3.25,4) node[big_] (B) {};
	\node[big_] (C) at (5.5,4) {};
	\draw[rounded corners] (-1,3) rectangle (6.5,5);
	%
	\begin{scope}[thepink,->]
		\draw[bend right=5] (a) to (1);
		\draw[bend right=10] (b) to (1);
		\draw[big>,bend left=25] (A) to (2);
		\draw[big>,bend left=20] (B) to (3);
		\draw[big>,bend left=15] (C) to (4);
	\end{scope}
\end{tikzpicture}
\qquad
\begin{tikzpicture}[x=5mm,y=5mm,octo]
	\node[circ] (1) at (.75,0) {};
	\node[big1] (2) at (2,0) {};
	\node[big1] (3) at (3.5,0) {};
	\node[big1] (4) at (5,0) {};
	%
	\draw ( 0  ,4) node[bullet] (a) {} -- ( 1  ,4) node[big_] (A) {};
	\draw ( 2.5,4) node[bullet] (b) {} -- ( 3.5,4) node[big_] (B) {};
	\draw ( 5  ,4) node[bullet] (c) {} -- ( 6  ,4) node[big_] (C) {};
	\draw[rounded corners] (-.5,3) rectangle (7,5);
	\path (0,-1) -- (1,-1);
	%
	\begin{scope}[thepink,->]
		\draw[bend right=5] (a) to (1);
		\draw[bend right=10] (b) to (1);
		\draw[bend right=15] (c) to (1);
		\draw[big>,bend left=25] (A) to (2);
		\draw[big>,bend left=20] (B) to (3);
		\draw[big>,bend left=15] (C) to (4);
	\end{scope}
\end{tikzpicture}
\]

### 2014-01-18 main/scratch.tex
added octopus roll lemma
hacks & fixes
explaining weight and constraint elements
finished informal description of encoding
re-wrote defn. "standard linking" (was: "natural linking")
added octopus arithmetic to "notation"

\documentclass{article}

\usepackage{amsthm}
\usepackage[round]{natbib}
\usepackage{mllequiv,willemtools}

@@

@@

>>>>

\documentclass[conference]{IEEEtran}

\usepackage{amsmath,amsthm}
\usepackage{mllequiv,willemtools}

\usepackage{pgffor}

@@

\[
\begin{tikzpicture}[x=-5mm,y=5mm,octo]
	\node[big_] (A) at (-1,2) {};
	\node[big1] (!) at (-1,0) {};
	\node at (.5,1) {$\Rightarrow$};
	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (5,2) -- (6,2) node[bullet] (c) {}; 
	\node[circ] (1) at (2,0) {}; \node[circ] (2) at (3,0) {}; \node[circ] (3) at (6,0) {};
	\draw[dotted] (4,2)--(5,2) (4,0)--(5.1,0);
	\begin{scope}[thepink,->]
			\draw[big>] (A) to (!.center);
			\draw[bend right=10] (a) to (1.center);
			\draw[bend right=10] (b) to (2.center);
			\draw[bend right=10] (c) to (3.center);
	\end{scope}
\end{tikzpicture}
\]

\[
\vc{
  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\draw (0,0) node[bullet] (a) {}--
		  (1,0) node[bullet] (b) {}--
		  (2,0) node[bullet] (c) {};
	\draw (4,0) node[bullet] (d) {}--
		  (5,0) node[bullet] (e) {}--
		  (6,0) node[bullet] (f) {}--
		  (7,0) node[bullet] (g) {};
	\foreach \i in {1,...,6} {\node[circ] (\i) at (\i,3) {};}
	\begin{scope}[thepink,->]
			\draw[bend right=10] (a) to (1);
			\draw[bend right=10] (b) to (2);
			\draw[bend right=10] (c) to (3);
			\draw[bend left=10]  (d) to (3);
			\draw[bend left=10]  (e) to (4);
			\draw[bend left=10]  (f) to (5);
			\draw[bend left=10]  (g) to (6);
	\end{scope}
  \end{tikzpicture}
}
\quad\Rightarrow\quad
\vc{
  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\node[big_] (A) at (-1,0) {$2'$};
	\node[big_] (B) at ( 1,0) {$3'$};
	\node[big1] (!) at ( 0,3) {$5'$};
	\begin{scope}[thepink,->,big>]
		\draw[bend right=15] (A) to (!);
		\draw[bend left=15]  (B) to (!);
	\end{scope}
  \end{tikzpicture}
}
\]

%
%\[
%\begin{tikzpicture}[x=5mm,y=-5mm,octo]
%	\draw (-1.75,0) node[bullet] (x) {} -- (-.75,0) node[bullet] (y) {}
%		  (  .75,0) node[bullet] (a) {} -- (1.75,0) node[bullet] (b) {}
%		  ( 3.25,0) node[bullet] (c) {} -- (4.25,0) node[bullet] (d) {};
%	\node[circ] (0) at (5.75,0) {};
%	\node[circ] (1) at (-1,3) {};
%	\node[circ] (2) at (1,3) {}; \node[circ] (3) at (2,3) {}; \node[circ] (4) at (3,3) {};
%	\draw[rounded corners] (0,2) rectangle (4,4);
%	\draw (4,3) -- (5,3) node[bullet] (e) {};
%	\begin{scope}[thepink,->]
%			\draw[bend right=10] (x) to (1.center);
%			\draw[bend right=20] (y) to (2.center);
%			\draw[bend right=10] (a) to (2.center);
%			\draw[bend right=10] (b) to (3.center);
%			\draw[bend left=10]  (c) to (3.center);
%			\draw[bend left=10]  (d) to (4.center);
%			\draw[bend right=10] (e) to (0.center);
%	\end{scope}
%\end{tikzpicture}
%\]

@@

\begin{frame}
	\octorollA1
\end{frame}

\begin{frame}
	\octorollB1
\end{frame}

\begin{frame}
	\octorollB2
\end{frame}

\begin{frame}
	\octorollB3
\end{frame}

\begin{frame}
	\octorollC
\end{frame}

\begin{frame}
	\octorollD1
\end{frame}
%
%\begin{frame}
%	\octorollE1
%\end{frame}
%
%\begin{frame}
%	\octorollE2
%\end{frame}
%
%\begin{frame}
%	\octorollE3
%\end{frame}
%
%\begin{frame}
%	\octorollE4
%\end{frame}
%
%\begin{frame}
%	\octorollE5
%\end{frame}
%
%\begin{frame}
%	\octorollE6
%\end{frame}
%
%\begin{frame}
%	\octorollE7
%\end{frame}

\begin{frame}
	\octorollD2
\end{frame}

\begin{frame}
	\octorollA2
\end{frame}

%\newcommand\octorollC{
%  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
%	\node[circ] (a1a) at (0,1.5) {}; \node[big1] (a1) at (-2,0) {}; \node[big1] (a2) at (0,0) {}; \node[big1] (a3) at (2,0) {};
%	\draw (-9  ,4) node[bullet] (d1a) {} -- (-8  ,4) node[big_] (d1) {};
%	\draw (-6.5,4) node[bullet] (d2a) {} -- (-5.5,4) node[big_] (d2) {};
%	\draw (-4  ,4) node[bullet] (d3a) {} -- (-3  ,4) node[big_] (d3) {};
%	\draw[rounded corners] (-10,3) rectangle (-2,5);
%	\draw (-2,4)--(-1,4) node[bullet] (d) {};
%	\draw ( 3  ,4) node[bullet] (e1a) {} -- ( 4  ,4) node[big_] (e1) {};
%	\draw ( 5.5,4) node[bullet] (e2a) {} -- ( 6.5,4) node[big_] (e2) {};
%	\draw ( 8  ,4) node[bullet] (e3a) {} -- ( 9  ,4) node[big_] (e3) {};
%	\draw[rounded corners] (10,3) rectangle (2,5);
%	\draw (2,4)--(1,4) node[bullet] (e) {};
%	\node[circ] (v1a) at (-4,8); \node[big1] (v1b) at (-3,8) {}; \node[big1] (v1c) at (-1.5,8) {};
%	\node[big1] (v2) at  ( 2.5,8) {}; \node[big1] (v2) at ( 2.5,8) {};
%	\draw[rounded corners] (-4.5,7) rectangle (-0.5,9);
%	\draw[rounded corners] ( 3.5,7) rectangle ( 0.5,9);
%	\draw (-0.5,8)--(0.5,8);
%	\node[circ] (v) at (0,6) {};
%	%
%	\begin{scope}[thepink,->]
%		\draw[bend left=15] (e) to (v);\draw[bend right=15] (d) to (v);
%		\draw[big>,bend right] (d1) to (v1); \draw[big>,bend right=20] (d2) to (v1); \draw[big>, bend right=20] (d3) to (v2);
%		\draw[bend right=15] (e1a) to (a1a); \draw[bend right=15] (e2a) to (a1a); \draw[bend right=15] (e3a) to (a1a); 
%		\draw[big>,bend right=20] (e1) to (a1);  \draw[big>,bend right=20] (e2) to (a2);  \draw[big>, bend right=20] (e3) to (a3);
%	\end{scope}
%  \end{tikzpicture}
%}

\[
	\big(\bigparr_{k\times c(v_i)}\big(\bigparr_{3i+2}1 \tn \bigparr_{3(n-i)+3}1\big) \big)\parr 1
\]
\[
	\big(\bigotimes_{k\times w(e)}\big(\bigotimes_{3i+2}\bot\parr\bigotimes_{3(j-i)+1}\bot\parr\bigotimes_{3(n-j)+3}\bot\big)\big)\tn\bot
\]

\[
	C = \bigparr(1^{3i+2}) \tn \bigparr(1^{3(n-i)+3})
\]

\[
	\big(\bigparr C^{k\times c(v_i)} \big)\parr 1
\]

\[
	W = \bigotimes(\bot^{3i+2})\parr\bigotimes(\bot^{3(j-i)+1})\parr\bigotimes(\bot^{3(n-j)+3}
\]

\[
	\big(\bigotimes W^{k\times w(e)}\big)\tn\bot
\]
